Lattices of acyclic pipe dreams

### 2023-03-17 acyclicFacets/draft/latticePipeDreams.tex
adding red and blue dots in brick polytope picture

\begin{example}
We have illustrated in \cref{fig:brickPolytope1,fig:brickPolytope2,fig:brickPolytope3} the brick polytopes of the subword complexes represented in \cref{fig:subwordComplex1,fig:subwordComplex2,fig:subwordComplex3}.
Note that the oriented graph (from bottom to top) defines a lattice in \cref{fig:brickPolytope1,fig:brickPolytope2} but not in \cref{fig:brickPolytope3}.
%
\begin{figure}[p]
	\centerline{\input{figures/brickPolytope1}}
	\caption{The brick polytope of~$\subwordComplex(Q,\wo)$ where~$Q = \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3$ in type~$A_3$. Its graph, oriented from bottom to top is the Hasse diagram of the lattice of \cref{fig:increasingFlipPosets}\,(left) and \cref{fig:subwordComplex1}. This is actually the $c$-associahedron and the $c$-Cambrian lattice for the Coxeter element~$c = \tau_2\tau_1\tau_3$ of type~$A_3$.}
	\label{fig:brickPolytope1}
\end{figure}
%
\begin{figure}[p]
	\centerline{\input{figures/brickPolytope2}}
	\caption{The brick polytope of~$\subwordComplex(Q,\wo)$ where~$Q = \tau_2 \tau_3 \tau_1 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_1$ in type~$A_3$. Its graph, oriented from bottom to top is the Hasse diagram of the lattice of \cref{fig:subwordComplex2}, but it is not obtained as a lattice quotient of the weak order.}
	\label{fig:brickPolytope2}
\end{figure}
%
\begin{figure}[p]
	\centerline{\input{figures/brickPolytope3}}
	\caption{The brick polytope of~$\subwordComplex(Q,\wo)$ where~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ in type~$A_3$. Its graph, oriented from bottom to top is the Hasse diagram of the poset of \cref{fig:increasingFlipPosets}\,(right) and \cref{fig:subwordComplex3}, which is not a lattice.}
	\label{fig:brickPolytope3}
\end{figure}
\end{example}

>>>>

\begin{example}
We have illustrated in \cref{fig:brickPolytope1,fig:brickPolytope2,fig:brickPolytope3} the brick polytopes of the subword complexes represented in \cref{fig:subwordComplex1,fig:subwordComplex2,fig:subwordComplex3}.
Note that the oriented graph (from bottom to top) defines a lattice in \cref{fig:brickPolytope1,fig:brickPolytope2} but not in \cref{fig:brickPolytope3}.
%
\begin{figure}[p]
	\centerline{\input{figures/brickPolytope1}}
	\caption{The brick polytope of~$\subwordComplex(Q,\wo)$ where~$Q = \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3 \tau_2 \tau_1 \tau_3$ in type~$A_3$. Its graph, oriented from bottom to top is the Hasse diagram of the lattice of \cref{fig:increasingFlipPosets}\,(left) and \cref{fig:subwordComplex1}. This is actually the $c$-associahedron and the $c$-Cambrian lattice for the Coxeter element~$c = \tau_2\tau_1\tau_3$ of type~$A_3$.}
	\label{fig:brickPolytope1}
\end{figure}
%
\begin{figure}[p]
	\centerline{\input{figures/brickPolytope2}}
	\caption{The brick polytope of~$\subwordComplex(Q,\wo)$ where~$Q = \tau_2 \tau_3 \tau_1 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_1$ in type~$A_3$. Its graph, oriented from bottom to top is the Hasse diagram of the lattice of \cref{fig:subwordComplex2}, but it is not obtained as a lattice quotient of the weak order.}
	\label{fig:brickPolytope2}
\end{figure}
%
\begin{figure}[p]
	\centerline{\input{figures/brickPolytope3}}
	\caption{The brick polytope of~$\subwordComplex(Q,\wo)$ where~$Q = \tau_1 \tau_2 \tau_3 \tau_2 \tau_1 \tau_2 \tau_3 \tau_2 \tau_1$ in type~$A_3$. Its graph, oriented from bottom to top is the Hasse diagram of the poset of \cref{fig:increasingFlipPosets}\,(right) and \cref{fig:subwordComplex3}, which is not a lattice (the two blue vertices have no join while the two red vertices have no meet).}
	\label{fig:brickPolytope3}
\end{figure}
\end{example}
